Title

### 2023-06-29 main.tex
I'm sorry.

\usepackage[english]{babel}
\usepackage{graphicx,helvet}
\usepackage{color}
\usepackage{url}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[inline]{showlabels}
\usepackage{bbm,bm}
\usepackage{soul}
\usepackage{amsfonts}
\usepackage{showlabels}

@@

% Title must be 250 characters or less.

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
\cpnote{Revisar}
Pauli channels are fundamental in the context of quantum computing as they
model noise in quantum devices.  We propose a quantum algorithm for simulating
Pauli channels on quantum computers 
and extend it to encompass Pauli dynamical maps 
(parametrized Pauli channels).
A parametrized quantum circuit is employed to accommodate for dynamical maps. 
We also establish the mathematical conditions for an
N-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is obtained. 
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}

\linenumbers

@@

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}. 
% Several 
% kinds of quantum systems have been simulated, like \cpnote{PONER ALGO ACA Y CITAR. 
% Te puedes inspirar en las introducciones de articulos que simulen sistemas cuanticos}. 
Being open quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts
towards the simulation of the evolution of open quantum
systems~\cite{cleve,Zanetti,Xin,Wei}.\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.}
\tbnote{Cambié un poco, agregué unos artículos que vi mucho más populares:}
{\color{purple} 
open quantum systems~\cite{Garcia, Wang,Weimer} and specifically for
quantum channels~\cite{Xin,Wei,Zanetti}.
}

@@

% }}}
% }}}
\section{Circuit for a Pauli Channel} % {{{
\label{sec: Circuit for a Pauli Channel}
% Intro {{{

@@

% }}}
% }}}
\section{One Parameter Circuits} % {{{
\label{sec: 1PR Circuits}

@@

% }}}

\section{Conclusion} % {{{

@@

% }}}

%\section{Supporting information} % {{{

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
% \paragraph*{S1 Fig.}
% \label{S1_Fig}
% {\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
% 
% \paragraph*{S2 Fig.}
% \label{S2_Fig}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 File.}
% \label{S1_File}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Table.}
% \label{S1_Table}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% }}}

\section{Acknowledgments} % {{{
Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.

@@

% }}}
\newpage
\appendix
%\input{Cosas-Escritas-Antes}

\end{document}

>>>>

\usepackage[english]{babel}
\usepackage{graphicx,helvet}
\usepackage{color}
\usepackage{url}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
% \usepackage[inline]{showlabels}
\usepackage{bbm,bm}
\usepackage{soul}
\usepackage{amsfonts}

@@

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
% \cpnote{Revisar}
Pauli channels are fundamental in the context of quantum computing as they
model the simplest kind of noise in quantum devices.  We propose a quantum
algorithm for simulating
Pauli channels 
and extend it to encompass Pauli dynamical maps 
(parametrized Pauli channels).
A parametrized quantum circuit is employed to accommodate for dynamical maps. 
We also establish the mathematical conditions for an
$N$-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is reported. 
% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}

% \linenumbers

@@

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts towards the
simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.

@@

% }}}
% }}}
\section{Circuit for a Pauli channel} % {{{
\label{sec: Circuit for a Pauli Channel}
% Intro {{{

@@

% }}}
% }}}
\section{One parameter circuits} % {{{
\label{sec: 1PR Circuits}

@@

% }}}
\section{Conclusion} % {{{

@@

% }}}
%\section{Supporting information} % {{{

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
% \paragraph*{S1 Fig.}
% \label{S1_Fig}
% {\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
% 
% \paragraph*{S2 Fig.}
% \label{S2_Fig}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 File.}
% \label{S1_File}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Table.}
% \label{S1_Table}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% }}}
\section{Acknowledgments} % {{{
Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.

@@

% }}}
\appendix
\end{document}
